### 2023-09-11 thesis/MSECE_thesis.tex
Finish data processing for ZCU ATC.

\section{Data Source(s)}
There are four datasets used in this work. The datasets are primarily speech corpora intended either for automatic speech recognition
research in the domain of aviation communications, linguistics research in aviation english, or both. As a result, the text-based data
samples that are used to train the language models in this work are transcripts of aural speech. The datasets used are described in more
detail below. All recordings and transcripts are in english, although there are multiple instances of foreign words occuring

@@

\subsection{Data Analysis}
% sequence lengths, unique tokens, total number of tokens, total number of samples, breakdown by each dataset
\begin{table}
    \centering
    \begin{tabular}{l c c c c}
        Corpus                         & Samples & Mean Sequence Length & Tokens  & Unique Tokens \\
        \toprule
        Air Traffic Control Complete   & 29,862  & 11.90                & 355,476 & 2,210         \\
        ATCO2                          & 874     & 12.46                & 10,886  & 855           \\
        Air Traffic Control Simulation & 9,544   & 11.29                & 107,759 & 824           \\
        ZCU CZ ATC Corpus              & 14,435  & 10.32                & 149,031 & 3106          \\
        \bottomrule
        Total                          & 54,715  & 11.39                & 623,152 & 5343          \\
    \end{tabular}
    \caption[short]{title}
\end{table}

\subsection{Preprocessing}
% explain and justify what is removed from the text, how, and why
% present and explain any relevant algorithms where necessary

>>>>

\section{Data Source(s)}\label{sec:data_source}
There are four datasets used in this work. The datasets are primarily speech corpora intended either for automatic speech recognition
research in the domain of aviation communications, linguistics research in aviation english, or both. As a result, the text-based data
samples that are used to train the language models in this work are transcripts of aural speech. The datasets used are described in more
detail below. All recordings and transcripts are in english, although there are multiple instances of foreign words occuring

@@

\section{Data Analysis}
% sequence lengths, unique tokens, total number of tokens, total number of samples, breakdown by each dataset
\begin{table}
    \centering
    \begin{tabular}{l r r r r}
        Corpus                         & Samples & Mean Sequence Length & Unique Tokens & Tokens  \\
        \toprule
        Air Traffic Control Complete   & 29,862  & 11.90                & 2,210         & 355,476 \\
        ATCO2                          & 874     & 12.46                & 855           & 10,886  \\
        Air Traffic Control Simulation & 9,544   & 11.29                & 824           & 107,759 \\
        ZCU CZ ATC Corpus              & 14,435  & 10.32                & 3,106         & 149,031 \\
        \bottomrule
        Total                          & 54,715  & 11.39                & 5,343         & 623,152 \\
    \end{tabular}
    \caption{Data statistics by corpus, including statistics across all corpora.}
\end{table}

\section{Data Processing}
All of the corpora listed above (see~\ref{sec:data_source}) are created at different times, for different purposes, and by different authors.
As a result, the data in these corpora all have different formats and need to be processed into a common format to be used together, with the goal
being to essentially create a super-corpus that includes all the corpora listed above.

All data was processed in Python using primarily built-in functions/modules\footnote{The \lstinline|re| and \lstinline|xml| modules were also used although
    these are built into most Python distributions by default.}. The text data is extracted from the corpus transcripts i.e.~Lisp in ATCC, XML in
ATCO2 and ZCU CZ ATC, and plain text in ATCOSIM, the transcriber annotations are removed where necessary\footnote{A copy of the original data is
    made, then the annotations are removed from the copy.}, and the resulting text is written in the standard corpus format (an ASCII text file with
one line in the file corresponding to one sample from the corpus) to a file.

\subsection{Data Preprocessing}
% explain and justify what is removed from the text, how, and why
% present and explain any relevant algorithms where necessary
